Chemistry of the Orphan Stream II: The First High-Resolution Spectroscopic Analysis on the Orphan Stream

### 2012-08-16 2012-oss-hrs/draft-oss.tex
added 2012 oss HRS paper folder

\shorttitle{First HRS Analysis on the Orphan Stream}
\shortauthors{Casey et al}

@@

\title{The First High-Resolution Spectroscopic Analysis on the Orphan Stream}

@@

\subsection{Stellar Parameters}

\subsubsection{Effective Temperature}

\subsubsection{Surface Gravity}

\subsection{Uncertainty Analysis}

\begin{deluxetable}{lcccccccccl}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
& \multicolumn{4}{c}{This work}  &
& \multicolumn{4}{c}{Literature} & \\
  \cline{2-5} \cline{7-10} \\
  \colhead{Star} &
  \colhead{$T_{\mbox{eff}}$} &
 \colhead{$\log{(g)}$} &
	\colhead{[Fe/H]} &
	\colhead{$v_t$} 
	&&
	\colhead{$T_{\mbox{eff}}$} &
	\colhead{$\log{(g)}$} &
	\colhead{[Fe/H]} &
	\colhead{$v_t$} &
	\colhead{Reference} \\
 & [K] & [dex] & [dex] & [km s$^{-1}$] 
&& [K] & [dex] & [dex] & [km s$^{-1}$] & 
}
\startdata
HD 136316 & $4370$ & $1.00$ & $-1.99$ & $1.95$ 
         && $4469$ & $1.29$ & $-1.74$ & $1.90$ & \citet{Gratton;et-al_2000} \\
HD 141531 & $4330$ & $0.90$ & $-1.74$ & $1.80$ 
         && $4335$ & $1.11$ & $-1.62$ & $1.50$ & \citet{Gratton;et-al_2000} \\
HD 142948 & $4870$ & $2.20$ & $-0.78$ & $1.45$ 
         && $4713$ & $2.17$ & $-0.77$ & $1.38$ & \citet{Gratton;et-al_2000} \\
HD 41667  & $4600$ & $1.70$ & $-1.23$ & $1.50$  
         && $4605$ & $1.88$ & $-1.16$ & $1.44$ & \citet{Gratton;et-al_2000} \\
HD 44007  & $4800$ & $1.80$ & $-1.77$ & $1.55$ 
         && $4850$ & $2.00$ & $-1.71$ & $2.20$ & \citet{Fulbright_2000} \\
HD 47536  & & & & 
         &&\nodata &\nodata & \nodata &\nodata & \\
HD 76932  & & & & 
         && $5900$ & $4.20$ & $-0.70$ & $1.25$ & \citet{Fulbright_2000} \\
HD 84903  & & & & 
         && $4500$ & $0.80$ & $-2.60$ & $2.00$ & \citet{Francois_1996} \\
HD 59984  & & & & 
         && & & & & Binary system.\\
HD 60060  & & & & 
         &&\nodata &\nodata & \nodata &\nodata & \\
HD 60228  & & & & 
         &&\nodata &\nodata & \nodata &\nodata & \\
OSS 1     & 5040 & 2.80 & -1.22 & 1.40 && & & & & \\
OSS 2     & 4550 & 0.80 & -1.78 & 1.85 && & & & & \\
OSS 3     & 4780 & 1.55 & -1.79 & 1.70 && & & & & \\
OSS 4     & 4580 & 0.80 & -2.75 & 2.05 && & & & & \\
OSS 5     & 5250 & 3.00 & -0.80 & 1.85 && & & & & 
\enddata
\end{deluxetable}

\begin{deluxetable}{lccccccccccccccccc}
\tablecolumns{18}
\tablewidth{\textwidth}
\tabletypesize{\scriptsize}
\tablecaption{Chemical Abundances\label{tab:stellar-parameters}}
\tablehead{
&  \multicolumn{5}{c}{OSS 1} & \colhead{} &
	\multicolumn{5}{c}{OSS 2} & \colhead{} &
	\multicolumn{5}{c}{OSS 3} \\
	\cline{2-6} \cline{8-12} \cline{14-18} \\
\colhead{Species} 
 & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
 & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
 & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$
}
\startdata
Na \textsc{I} & ? & ? & ? & ? & ?
             && $4.21$ & $-2.03$ &    $-0.23$ &   $3$ & $0.05$
             && $4.42$ & $-1.82$ &    $-0.03$ &   $3$ & $0.07$  \\
Mg \textsc{I} & $6.56$ & $-1.04$ & \phs$0.16$ &   $4$ & $0.10$  
             && $5.90$ & $-1.70$ & \phs$0.10$ &   $6$ & $0.10$   
             && $5.95$ & $-1.65$ & \phs$0.15$ &   $5$ & $0.05$  \\
Si \textsc{I} & $6.57$ & $-0.94$ & \phs$0.26$ &   $4$ & $0.23$
             && $5.66$ & $-1.85$ &    $-0.05$ &   $3$ & $0.26$   
             && $6.20$ & $-1.31$ & \phs$0.43$ &   $3$ & $0.16$  \\
Ca \textsc{I} & $5.48$ & $-0.86$ & \phs$0.34$ &  $14$ & $0.14$
             && $4.79$ & $-1.55$ & \phs$0.25$ &  $17$ & $0.12$   
             && $4.87$ & $-1.47$ & \phs$0.32$ &  $18$ & $0.09$  \\
Ti \textsc{I} & $3.73$ & $-1.22$ &    $-0.02$ &  $21$ & $0.15$  
             && $3.00$ & $-1.95$ &    $-0.15$ &  $20$ & $0.16$   
             && $3.13$ & $-1.82$ &    $-0.03$ &  $23$ & $0.09$  \\
Ti \textsc{II}& $3.91$ & $-1.04$ & \phs$0.16$ &  $25$ & $0.10$  
             && $3.19$ & $-1.76$ & \phs$0.04$ &  $23$ & $0.14$   
             && $3.36$ & $-1.59$ & \phs$0.20$ &  $24$ & $0.09$  \\
Fe \textsc{I} & $6.24$ & $-1.26$ &    \nodata & $149$ & $0.16$  
             && $5.71$ & $-1.79$ &    \nodata & $112$ & $0.16$  
             && $5.71$ & $-1.79$ &    \nodata & $154$ & $0.12$  \\
Fe \textsc{II}& $6.19$ & $-1.21$ & \phs$0.05$ &  $15$ & $0.16$
             && $5.75$ & $-1.75$ &    $-0.04$ &   $8$ & $0.10$   
             && $5.71$ & $-1.79$ & \phs$0.00$ &  $20$ & $0.16$  \\

\\ & \multicolumn{5}{c}{OSS 4} && \multicolumn{5}{c}{OSS 5} \\
     \cline{2-6} \cline{8-12} \\
Na \textsc{I} & $3.69$ & $-2.55$ & \phs$0.20$ &  $2$ & $0.04$
             && $5.17$ & $-1.07$ &    $-0.27$ &  $4$ & $0.13$ \\ 
Mg \textsc{I} & $5.11$ & $-2.49$ & \phs$0.26$ &  $7$ & $0.13$
             && $6.70$ & $-0.90$ &    $-0.10$ &  $5$ & $0.15$ \\
Si \textsc{I} & $5.38$ & $-2.13$ & \phs$0.62$ &  $3$ & $0.03$
             && $6.78$ & $-0.73$ & \phs$0.07$ &  $4$ & $0.07$ \\
Ca \textsc{I} & $3.75$ & $-2.59$ & \phs$0.16$ &  $9$ & $0.10$
             && $5.77$ & $-0.57$ & \phs$0.23$ & $10$ & $0.12$ \\
Ti \textsc{I} & $2.28$ & $-2.67$ & \phs$0.08$ & $13$ & $0.15$
             && $4.26$ & $-0.69$ & \phs$0.11$ & $15$ & $0.36$ \\
Ti \textsc{II}& $2.31$ & $-2.64$ & \phs$0.11$ & $24$ & $0.15$
             && $4.28$ & $-0.67$ & \phs$0.13$ & $13$ & $0.19$ \\
Fe \textsc{I} & $4.74$ & $-2.76$ &    \nodata & $89$ & $0.11$
             && $6.68$ & $-0.82$ &    \nodata & $99$ & $0.18$ \\
Fe \textsc{II}& $4.77$ & $-2.73$ & \phs$0.03$ & $13$ & $0.12$
             && $6.71$ & $-0.79$ &    $-0.03$ & $14$ & $0.16$ \\
\enddata
\end{deluxetable}

\section{Abundances}

\section{Discussion}

\section{Results}

\section{Conclusions}

>>>>

\shorttitle{Chemistry of the Orphan Stream II}
\shortauthors{Casey et al}

@@

\title{Chemistry of the Orphan Stream II: The First High-Resolution Spectroscopic Analysis on the Orphan Stream}

@@

\newpage

\begin{deluxetable*}{lcccccccccl}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
& \multicolumn{4}{c}{This work}  &
& \multicolumn{4}{c}{Literature} & \\
  \cline{2-5} \cline{7-10} \\
  \colhead{Star} &
  \colhead{$T_{\mbox{eff}}$} &
 \colhead{$\log{(g)}$} &
	\colhead{[Fe/H]} &
	\colhead{$v_t$} 
	&&
	\colhead{$T_{\mbox{eff}}$} &
	\colhead{$\log{(g)}$} &
	\colhead{[Fe/H]} &
	\colhead{$v_t$} &
	\colhead{Reference} \\
 & [K] & [dex] & [dex] & [km s$^{-1}$] 
&& [K] & [dex] & [dex] & [km s$^{-1}$] & 
}
\startdata
HD 136316 & $4370$ & $1.00$ & $-1.99$ & $1.95$ 
         && $4469$ & $1.29$ & $-1.74$ & $1.90$ & \citet{Gratton;et-al_2000} \\
HD 141531 & $4330$ & $0.90$ & $-1.74$ & $1.80$ 
         && $4335$ & $1.11$ & $-1.62$ & $1.50$ & \citet{Gratton;et-al_2000} \\
HD 142948 & $4870$ & $2.20$ & $-0.78$ & $1.45$ 
         && $4713$ & $2.17$ & $-0.77$ & $1.38$ & \citet{Gratton;et-al_2000} \\
HD 41667  & $4600$ & $1.70$ & $-1.23$ & $1.50$  
         && $4605$ & $1.88$ & $-1.16$ & $1.44$ & \citet{Gratton;et-al_2000} \\
HD 44007  & $4800$ & $1.80$ & $-1.77$ & $1.55$ 
         && $4850$ & $2.00$ & $-1.71$ & $2.20$ & \citet{Fulbright_2000} \\
HD 47536  & & & & 
         &&\nodata &\nodata & \nodata &\nodata & \\
HD 76932  & & & & 
         && $5900$ & $4.20$ & $-0.70$ & $1.25$ & \citet{Fulbright_2000} \\
HD 84903  & & & & 
         && $4500$ & $0.80$ & $-2.60$ & $2.00$ & \citet{Francois_1996} \\
HD 59984  & & & & 
         && & & & & Binary system.\\
HD 60060  & & & & 
         &&\nodata &\nodata & \nodata &\nodata & \\
HD 60228  & & & & 
         &&\nodata &\nodata & \nodata &\nodata & \\
OSS 1     & 5040 & 2.80 & -1.22 & 1.40 && & & & & \\
OSS 2     & 4550 & 0.80 & -1.78 & 1.85 && & & & & \\
OSS 3     & 4780 & 1.55 & -1.79 & 1.70 && & & & & \\
OSS 4     & 4580 & 0.80 & -2.75 & 2.05 && & & & & \\
OSS 5     & 5250 & 3.00 & -0.80 & 1.85 && & & & & 
\enddata
\end{deluxetable*}

\newpage
\newpage

\newpage
\newpage

\begin{deluxetable*}{lccccccccccccccccc}
\tablecolumns{18}
\tablewidth{\textwidth}
\tabletypesize{\scriptsize}
\tablecaption{Standard Star Chemistries\label{tab:stellar-parameters}}
\tablehead{
&  \multicolumn{5}{c}{HD 142948} & \colhead{} &
	\multicolumn{5}{c}{HD 141531} & \colhead{} &
	\multicolumn{5}{c}{HD 44007} \\
	\cline{2-6} \cline{8-12} \cline{14-18} \\
\colhead{Species} 
 & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
 & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
 & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$
}
\startdata

Na \textsc{I} & 5.99 & $-$0.25 & \phn0.53 &  1 & \nodata\tablenotemark{a} % HD 142948
             && 4.56 & $-$1.68 & \phn0.04 &  2 & 0.07    % HD 141531
             && 4.53 & $-$1.71 & \phn0.06 &  3 & 0.05 \\ % HD 44007
Mg \textsc{I} & 7.21 & $-$0.39 & \phn0.39 &  4 & 0.06
             && 6.26 & $-$1.34 & \phn0.38 &  4 & 0.12
             && 6.16 & $-$1.44 & \phn0.33 &  3 & 0.04 \\
O \textsc{I}  & 8.54 & $-$0.15 & \phn0.63 &  2 & 0.05
             && 7.51 & $-$1.18 & \phn0.54 &  2 & \phn0.00\tablenotemark{a}
             && 7.50 & $-$1.19 & \phn0.58 &  1 & \nodata\tablenotemark{a} \\
Si \textsc{I} & 6.67 & $-$0.84 &  $-$0.06 &  2 & 0.07
             && 5.86 & $-$1.65 & \phn0.07 &  3 & 0.20
             && 6.19 & $-$1.32 & \phn0.45 &  3 & \phn0.02\tablenotemark{a} \\
Ca \textsc{I} & 5.83 & $-$0.51 & \phn0.27 &  8 & 0.07
             && 4.91 & $-$1.43 & \phn0.29 & 12 & 0.09
             && 5.02 & $-$1.32 & \phn0.45 & 16 & 0.08 \\
Ti \textsc{I} & 4.26 & $-$0.69 & \phn0.09 & 15 & 0.11
             && 3.09 & $-$1.86 &  $-$0.14 & 19 & 0.11
             && 3.32 & $-$1.63 & \phn0.14 & 19 & 0.08 \\
Ti \textsc{II}& 4.53 & $-$0.42 & \phn0.36 & 18 & 0.11
             && 3.53 & $-$1.42 & \phn0.30 & 22 & 0.11
             && 3.50 & $-$1.45 & \phn0.32 & 32 & 0.12 \\        
Sc \textsc{II}& ?    &   ?     &    ?     &  ? &  ?
             && 1.60 & $-$1.55 & \phn0.17 &  7 & \phn0.04\tablenotemark{a}
             && 1.46 & $-$1.69 & \phn0.08 &  9 & 0.06 \\
Fe \textsc{I} & 6.72 & $-$0.78 & \phn0.00 & 104& 0.14
             && 5.78 & $-$1.72 & \phn0.00 & 100& 0.11
             && 5.72 & $-$1.78 & \phn0.00 & 135& 0.10 \\
Fe \textsc{II}& 6.73 & $-$0.77 & \phn0.01 & 13 & 0.18
             && 5.86 & $-$1.64 & \phn0.08 & 11 & 0.10
             && 5.70 & $-$1.80 &  $-$0.02 & 14 & 0.11 \\
V \textsc{I}  & 6.27 &\phn2.34 & \phn3.12 &  2 & \phn0.02\tablenotemark{a}
             && 4.69 &\phn0.76 & \phn2.50 &  2 & 0.22
             && 4.63 &\phn0.70 & \phn2.47 &  3 & \phn0.04\tablenotemark{a} \\
Cr \textsc{I} & 4.66 & $-$0.98 &  $-$0.20 &  6 & 0.07
             && 3.61 & $-$2.03 &  $-$0.29 & 10 & 0.08
             && 3.67 & $-$1.97 &  $-$0.20 & 13 & 0.06 \\
Cr \textsc{II}& 4.83 & $-$0.81 &  $-$0.03 &  3 & \phn0.04\tablenotemark{a}
             && 4.06 & $-$1.58 & \phn0.16 &  2 & 0.07
             && 4.00 & $-$1.64 & \phn0.13 &  5 & 0.05 \\
Mn \textsc{I} & 4.98 & $-$0.45 & \phn0.33 &  4 & 0.12
             && 3.72 & $-$1.71 & \phn0.03 &  5 & 0.18
             && 3.44 & $-$1.99 &  $-$0.22 &  6 & 0.22 \\
Co \textsc{I} & 4.06 & $-$0.93 &  $-$0.15 &  3 & \phn0.01\tablenotemark{a}
             && 2.97 & $-$2.02 &  $-$0.28 &  3 & 0.15
             && 3.13 & $-$1.86 &  $-$0.09 &  4 & 0.10 \\
Ni \textsc{I} & 5.52 & $-$0.70 & \phn0.08 &  8 & 0.08
             && 4.33 & $-$1.89 &  $-$0.15 & 13 & 0.09
             && 4.34 & $-$1.88 &  $-$0.11 & 13 & 0.09 \\
\enddata
\tablenotetext{a}{Minimum uncertainty of $\pm$0.05 dex adopted for this measurement.}
\end{deluxetable*}

\newpage
\newpage

\begin{deluxetable*}{lccccccccccccccccc}
\tablecolumns{18}
\tablewidth{\textwidth}
\tabletypesize{\scriptsize}
\tablecaption{Orphan Stream Chemistry\label{tab:stellar-parameters}}
\tablehead{
&  \multicolumn{5}{c}{OSS 1} & \colhead{} &
	\multicolumn{5}{c}{OSS 2} & \colhead{} &
	\multicolumn{5}{c}{OSS 3} \\
	\cline{2-6} \cline{8-12} \cline{14-18} \\
\colhead{Species} 
 & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
 & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
 & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$
}
\startdata
Na \textsc{I} & ? & ? & ? & ? & ?                              % OSS 1
             && $4.21$ & $-2.03$ &    $-0.23$ &   $3$ & $0.05$ % OSS 2
             && $4.42$ & $-1.82$ &    $-0.03$ &   $3$ & $0.07$ % OSS 3
             \\
Mg \textsc{I} & $6.56$ & $-1.04$ & \phs$0.16$ &   $4$ & $0.10$  
             && $5.90$ & $-1.70$ & \phs$0.10$ &   $6$ & $0.10$   
             && $5.95$ & $-1.65$ & \phs$0.15$ &   $5$ & $0.05$  \\
Si \textsc{I} & $6.57$ & $-0.94$ & \phs$0.26$ &   $4$ & $0.23$
             && $5.66$ & $-1.85$ &    $-0.05$ &   $3$ & $0.26$   
             && $6.20$ & $-1.31$ & \phs$0.43$ &   $3$ & $0.16$  \\
Ca \textsc{I} & $5.48$ & $-0.86$ & \phs$0.34$ &  $14$ & $0.14$
             && $4.79$ & $-1.55$ & \phs$0.25$ &  $17$ & $0.12$   
             && $4.87$ & $-1.47$ & \phs$0.32$ &  $18$ & $0.09$  \\
Ti \textsc{I} & $3.73$ & $-1.22$ &    $-0.02$ &  $21$ & $0.15$  
             && $3.00$ & $-1.95$ &    $-0.15$ &  $20$ & $0.16$   
             && $3.13$ & $-1.82$ &    $-0.03$ &  $23$ & $0.09$  \\
Ti \textsc{II}& $3.91$ & $-1.04$ & \phs$0.16$ &  $25$ & $0.10$  
             && $3.19$ & $-1.76$ & \phs$0.04$ &  $23$ & $0.14$   
             && $3.36$ & $-1.59$ & \phs$0.20$ &  $24$ & $0.09$  \\
Fe \textsc{I} & $6.24$ & $-1.26$ &    \nodata & $149$ & $0.16$  
             && $5.71$ & $-1.79$ &    \nodata & $112$ & $0.16$  
             && $5.71$ & $-1.79$ &    \nodata & $154$ & $0.12$  \\
Fe \textsc{II}& $6.19$ & $-1.21$ & \phs$0.05$ &  $15$ & $0.16$
             && $5.75$ & $-1.75$ &    $-0.04$ &   $8$ & $0.10$   
             && $5.71$ & $-1.79$ & \phs$0.00$ &  $20$ & $0.16$  \\
Sc \textsc{II}&&&&&  % OSS 1
             && $1.10$ & $-2.05$ &    $-0.27$ &   $7$ & $0.07$ 
             && $1.25$ & $-1.90$ &    $-0.11$ &  $10$ & $0.10$ \\
V \textsc{I}  &&&&&  % OSS 1
             && $4.50$ & \phs$0.57$ & $-1.21$ &   $4$ & $0.17$ 
             && $4.57$ & \phs$0.64$ & $-1.15$ &   $3$ & $0.03$ \\
Cr \textsc{I} &&&&&  % OSS 1
             && $3.63$ & $-2.01$ &    $-0.23$ &  $12$ & $0.08$ 
             && $3.63$ & $-2.01$ &    $-0.22$ &  $15$ & $0.11$ \\
Cr \textsc{II}&&&&&  % OSS 1
             && $3.81$ & $-1.83$ &    $-0.05$ &   $3$ & $0.11$ 
             && $3.99$ & $-1.65$ & \phs$0.14$ &   $3$ & $0.04$ \\
Mn \textsc{I} &&&&&  % OSS 1
             && $3.42$ & $-2.01$ &    $-0.23$ &   $4$ & $0.04$ 
             && $3.41$ & $-2.02$ &    $-0.23$ &   $6$ & $0.14$ \\
Co \textsc{I} &&&&&  % OSS 1
             && $3.14$ & $-1.85$ &    $-0.07$ &   $3$ & $0.19$ 
             && $3.00$ & $-1.99$ &    $-0.20$ &   $5$ & $0.17$ \\
Ni \textsc{I} &&&&&  % OSS 1
             && $4.24$ & $-1.98$ &    $-0.20$ &   $7$ & $0.07$ 
             && $4.32$ & $-1.90$ &    $-0.11$ &  $13$ & $0.12$ \\

\\ & \multicolumn{5}{c}{OSS 4} && \multicolumn{5}{c}{OSS 5} \\
     \cline{2-6} \cline{8-12} \\
Na \textsc{I} & $3.69$ & $-2.55$ & \phs$0.20$ &  $2$ & $0.04$
             && $5.17$ & $-1.07$ &    $-0.27$ &  $4$ & $0.13$ \\ 
Mg \textsc{I} & $5.11$ & $-2.49$ & \phs$0.26$ &  $7$ & $0.13$
             && $6.70$ & $-0.90$ &    $-0.10$ &  $5$ & $0.15$ \\
Si \textsc{I} & $5.38$ & $-2.13$ & \phs$0.62$ &  $3$ & $0.03$
             && $6.78$ & $-0.73$ & \phs$0.07$ &  $4$ & $0.07$ \\
Ca \textsc{I} & $3.75$ & $-2.59$ & \phs$0.16$ &  $9$ & $0.10$
             && $5.77$ & $-0.57$ & \phs$0.23$ & $10$ & $0.12$ \\
Ti \textsc{I} & $2.28$ & $-2.67$ & \phs$0.08$ & $13$ & $0.15$
             && $4.26$ & $-0.69$ & \phs$0.11$ & $15$ & $0.36$ \\
Ti \textsc{II}& $2.31$ & $-2.64$ & \phs$0.11$ & $24$ & $0.15$
             && $4.28$ & $-0.67$ & \phs$0.13$ & $13$ & $0.19$ \\
Fe \textsc{I} & $4.74$ & $-2.76$ &    \nodata & $89$ & $0.11$
             && $6.68$ & $-0.82$ &    \nodata & $99$ & $0.18$ \\
Fe \textsc{II}& $4.77$ & $-2.73$ & \phs$0.03$ & $13$ & $0.12$
             && $6.71$ & $-0.79$ &    $-0.03$ & $14$ & $0.16$ \\
\enddata
\end{deluxetable*}

\newpage
\newpage

\newpage
\newpage
